### 2024-01-14 documentation/thesis/thesis_document.tex
more thesis

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri}
scanners.\cite{Hori2021-pt}

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field MRI is the improved imaging of
soft tissues, especially when examining joints and muscles. It also
offers more cost-effective alternatives to high-field MRI
systems.\cite{Hori2021-pt}

@@

@@

The shimming process is a crucial step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is crucial for high-resolution and
artifact-free images.\cite{10.3389/fphy.2021.704566}

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field. Software
shimming, on the other hand, uses algorithms to adjust the control
parameters of the \gls{mri} system and improve
homogeneity.\cite{10.3389/fphy.2021.704566}

In this work, reference is made exclusively to the hardware shim
process. Since this project is to be used in the future to construct a
low-field \gls{mri} B0 field magnet from permanent magnets.

@@

\begin{itemize}
\item
  zeigt ansätzte einfacher magnet vermesseungen
  \cite{Wickenbrock_2021}
\item
  contruction of hallbach ringe \cite{cmr.a.20165}
\end{itemize}

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference \ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the
\passthrough{\lstinline!readout!}
command\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}
\ref{software-readout-framework}-library. The serial interface is also
used here. However, after a connection attempt by the
\passthrough{\lstinline!MRPHal!}\ref{hal} module of the \gls{mrp}
\ref{software-readout-framework}-library, the system switches to binary
mode, which is initiated using the \passthrough{\lstinline!sbm!}
command. The same commands are available as for \gls{cli}-based
communication.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} and the
following software settings:

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \passthrough{\lstinline!got pulse within 1000ms!} and this
becomes the \passthrough{\lstinline!primary!} sensor. This means that in
a chain of sensors there is exactly one
\passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the
\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
command. An important aspect of the implementation here was that there
is no numbering or sequence of the individual sensors. This means that
for the subsequent readout of the measurements, it is only important
that they are taken at the same interval across all sensors. The sensor
differentiation takes place later in the \gls{mrp}
\ref{software-readout-framework}-library by using the sensor \gls{uuid}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - e.g.~from hardware sensors \ref{unified-sensor}
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyze different data sets \ref{analysis}
\end{itemize}

@@

As the following, this concept is referred to as
\passthrough{\lstinline!user interaction points!}\ref{user-interaction-points}
and is explained in the following chapter.

@@

A project called
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
implements a data analysis step and optimizes a magnetic field that is
as homogeneous as possible within a circular section using given
mechanical dimensions as input parameters of the magnets used. For this
purpose, a mutation of the magnet positions and rotations is performed.
The result is a list of positions for each magnet.

The
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
opensource project, can generate basic \gls{cad} drawings for \gls{mri}
magnets in a Hallbach configuration. To do this, the number of magnets
and additional parameters for the properties of the \gls{cad} model to
be created are passed to the function provided as input parameters using
a \gls{json} file. The result is then an
\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} based 3D model of
the magnet holder.

@@

The input parameters of the
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. We assume ideal magnets here. However, it should
also be possible to import field data in a more measured form later on.
Using the DataAquisition sub-step, it is possible to generate any number
of ideal magnets.

@@

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the
\passthrough{\lstinline!HalbachOptimization!}\cite{HalbachOptimization}
project, the function signature of the start function must be changed.
This receives the result of the previous step, in this case the
generated magnet data. By optionally setting meta data in the universal
bilbiothekt data type, constants can be replaced in the analysis
function and made dynamically configurable. The return result also
corresponds to this data type so that subsequent steps are compatible
and contains the magnet data with modified position and rotation data.

@@

The last step is to call up the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner}
project, which creates the \gls{cad} model of the magnet holder. The
data can also be exported as files here. To make the project compatible,
the function signatures are also adapted here. In this case, more
changes are required, as the configuration file is loaded from the file
system. This logic must be removed in order to use the added meta data
in the input parameter instead.

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}\cite{HalbachMRIDesigner},
the other steps can simply be preserved and only the new step needs to
be implemented.

@@

In each of these categories there are then several sub-categories
divided into User Interaction Points. An overview of these is given in
the subchapters as the following. There are also introductory examples
which provide an overview of the basic functions in the
\passthrough{\lstinline!Examples!}\ref{examples} section, as well as
further examples in the online
documentation\cite{MagneticReadoutProcessingReadTheDocs}.

@@

The system is also designed to be compatible with
\passthrough{\lstinline!Extension Modules!}\ref{extension-modules},
allowing the generation of measurement data through various modules.
This extensibility enhances the versatility of the system, accommodating
diverse measurement scenarios and expanding its utility across different
domains.

@@

\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:54:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

@@

Since there are popular data processing frameworks such as
Numpy\cite{harris2020array}, or the program for mathematical
calculations, Matlab are often used, the library also supports export
formats for these systems.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!.dump()!} - \gls{json}
\item
  \passthrough{\lstinline!.to\_numpy\_matrix()!} - Numpy-Array of
  \passthrough{\lstinline!data!} object with different options
\item
  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
  measurement values and temperatures
\end{itemize}

Currently, data re-import of an exported measurement is only supported
via the \gls{json} format, as an export using the other options (Numpy,
Matlab)loses data during the export procedure.

@@

Another collection of optional modules provided by the library is the
connection of external hardware sensors. All compatible sensors that are
compatible with the firmware developed in the
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
supported here. The library provides the following sensor \gls{hal}
modules for this purpose:

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
  sensors such as
  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
\item
  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
\end{itemize}

@@

On the one hand, it is possible with the
\passthrough{\lstinline!MRPVisualization!} module to display measurement
data as a table or streamplot, lineplot. This makes it possible, for
example, to visually identify outliers or trends in the measurement
data. These can also be saved as an image file. The module is compatible
with all measurement data.

In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
module, this provides functions to create 2D map plots a polar
coordinate system. This requires measurement data with additionally set
spatial coordinates. These can be generated automatically with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
the user must provide the spatial information from another source.

@@

In addition, the export function
\passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
of the data in the
\passthrough{\lstinline!Numpy!}\cite{harris2020array} framework, in
which many other standard analysis functions are implemented.

@@

The \passthrough{\lstinline!MRPProxy!}\ref{MRPlib_Proxy_Module.png}
module has been developed to allow forwarding and interaction with
several sensors over a network connection using a \gls{rest} interface.

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the \passthrough{\lstinline!control!}
\gls{pc}, only the \gls{ip} address or hostname of the \gls{pc} running
an \passthrough{\lstinline!MRPProxy!} instance is
required\ref{lst:mrpcli_config_using_rpc}.

@@

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality\cite{PTPIEEE1588} can be used on
many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
when the \passthrough{\lstinline!info!}\ref{lst:mtsc} command is
received over network.

@@

For commands where there are several entries for
\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}\ref{Sensor_capabilities_merging.csv},
there are two possible approaches to how the command is processed:

@@

The \passthrough{\lstinline!extend commands using an id parameter!}
strategy is used for different sensors. Each command is extended on the
\passthrough{\lstinline!Network-Proxy!}\ref{network-proxy} by another
\gls{uuid} parameter, according to the following scheme:

@@

After generating simple measurements with random values in the previous
example \ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the \passthrough{\lstinline!MRPHal!} module was
developed, which can interact with all
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor}-compatible
sensors. In the following example \ref{lst:mrpexample_hal}, an
\passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor} is
connected locally to the host \gls{pc}.

@@

If no hardware sensor is available or for the generation of test data,
the \passthrough{\lstinline!MRPSimulation!} module is available. This
contains a series of functions that simulate various magnets and their
fields. The result is a complete \passthrough{\lstinline!MRPReading!}
measurement with a wide range of set meta data. The example
\ref{lst:mrpexample_simulation} illustrated the basic usage. Different
variations of the \passthrough{\lstinline!generate\_reading!} function
offers the user additional parameterisation options, such as random
polarisation direction or a defined centre-of-gravity vector. The data
is generated in the background using the
\passthrough{\lstinline!magpylib!}\cite{ortner2020magpylib} library
according to the specified parameters.

@@

Once data can be acquired using hardware or software sensors, the next
step is to analyse this data. \gls{mrp} provides some simple analysis
functions for this purpose. The code example shows the basic use of the
module. The \textbf{Evaluation}\ref{evaluation} chapter shows how the
user can implement their own algorithms and add them to the library.

@@

This final example shows the use of the MRP Visualisation module, which
provides general functions for visualising measurements. This makes it
possible to visually assess the results of a measurement. This is
particularly helpful for full-sphere measurements recorded with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor. The
sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
designed for these. The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement.

@@

The following example code \ref{lst:mrpexample_hallbach}, shows how a
simple hallbach magnetic ring can be generated. Eight random
measurements are generated here. It is important that the magnet type
(here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is specified. This
is necessary so that the correct magnet cutouts can be generated when
creating the 3D model. After the measurements have been generated, they
are provided with a position and rotation offset according to the
Hallbach design and calucation
scheme\cite{HallbachMagnetDesignPaper} using the
\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!}\cite{OpenSCAD} file, which
contains the module generated. After computing the model using the
\passthrough{\lstinline!OpenSCAD!}-\gls{cli} utility, the following
model rendering
\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
can be generated.

@@

In the other scenario, the tests are to be carried out before a new
release in the repository on the basis of
\passthrough{\lstinline!Github Actions!}\cite{GithubActions}. Here
there is the possibility to host local runner software, which then has
access to the hardware, but then a \gls{pc} must be permanently
available for this task. Instead, the hardware sensors were simulated by
software and executed via virtualisation on the systems provided by
\passthrough{\lstinline!Github Actions!}\cite{GithubActions}.

>>>>

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field MRI is the improved imaging of
soft tissues, especially when examining joints and muscles. It also
offers more cost-effective alternatives to high-field MRI systems
\cite{Hori2021-pt}.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
\caption{Example hallbach ring magnet with cutouts for eight cubical
permanent magnets
\label{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}}
\end{figure}

Halbach ring magnets \cite{Halbach1980DesignOP} have become a common
design for low field \gls{mri} and \gls{nmr} systems
\cite{cmr.a.20165}.

They have the ability to generate extremely homogeneous magnetic flux
densities, produce virtually no stray fields and are particularly
attractive for larger magnets as their design has the best flux-to-mass
ratio \cite{Wickenbrock_2021}.

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
shows an example \gls{cad} model of such a ring, in which in this case
eight cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
generate homogeneous magnetic flux densities of around
\passthrough{\lstinline!20mT!}.

The homogeneity in this configuration depends, among other things, on
the following aspects:

\begin{itemize}
\item
  \textbf{Material}

  The magnetic properties of a material influence the generated field
  strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}

  The orientation of the magnetic moments in the material influences the
  field strength. A higher magnetization leads to a stronger field
  strength.
\item
  \textbf{Temperature}

  Temperature can influence the magnetic properties of a material. The
  magnetization of some materials decreases with increasing temperature.
\item
  \textbf{Manufacturing process}

  The manufacturing process can influence the magnetic properties of the
  material. This is dependent on the purity of the starting materials
  used and the processing methods. There may also be deviations in field
  strength if different magnets from different production batches are
  compared.
\end{itemize}

These aspects can also be applied to individual magnets. As a result,
this also complicates the effect on the structure of a Halbach ring
magnet. If these are joined together to form a ring, positioning
tolerances are also added.

In order to compensate for inhomogeneities in a finished system, there
are various so-called shimming procedures which further improve
homogeneity after the system has been assembled.

@@

The shimming process is a crucial step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is crucial for high-resolution and
artifact-free images \cite{10.3389/fphy.2021.704566}.

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field. Software
shimming, on the other hand, uses algorithms to adjust the control
parameters of the \gls{mri} system and improve homogeneity
\cite{10.3389/fphy.2021.704566}.

In this work, reference is made exclusively to the hardware shim
process. Since this project is to be used in the future to construct a
low-field \gls{mri} field magnet from permanent magnets.

@@

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known.

As a result, there is the possibility of using the shimming process or
checking the permanent magnets used in advance before they are used in a
Hallbach configuration.

There are two ways of using the data from the magnets that were
previously measured:

\begin{itemize}
\tightlist
\item
  By using binning or sorting algorithms to filter for the most similar
  magnets
\item
  Adjustment of the rotation and position within the Hallbach
  configuration
\end{itemize}

\cite{Wickenbrock_2021}

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference \ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the
\passthrough{\lstinline!readout!} command
\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}
\ref{software-readout-framework}-library. The serial interface is also
used here. However, after a connection attempt by the \gls{hal}
\ref{mrphal} module of the \gls{mrp}
\ref{software-readout-framework}-library, the system switches to binary
mode, which is initiated using the \passthrough{\lstinline!sbm!}
command. The same commands are available as for \gls{cli}-based
communication, but in a binary format.

@@

The table
shows\ref{Measured_sensor_readout_to_processing_using_host_software.csv}
shows various jitter measurements. These were performed on a
\passthrough{\lstinline!RaspberryPi 4 4GB!}-\gls{sbc} together with an
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} and
the following software settings:

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \passthrough{\lstinline!register irq on sync pin!} is
overwritten. To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout branch
condition \passthrough{\lstinline!got pulse within 1000ms!} and this
becomes the \passthrough{\lstinline!primary!} sensor. This means that in
a chain of sensors there is exactly one
\passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} branch result. The
synchronisation status can be queried via the user interface
\ref{communication-interface} using the \passthrough{\lstinline!opmode!}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here was that there is no numbering or sequence of the
individual sensors. This means that for the subsequent readout of the
measurements, it is only important that they are taken at the same
interval across all sensors. The sensor differentiation takes place
later in the \gls{mrp} \ref{software-readout-framework}-library by using
the sensor \gls{uuid}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - from hardware sensors \ref{unified-sensor} or other
  data sources
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyze different data sets \ref{analysis}
\end{itemize}

@@

As the following, this concept is referred to as
\passthrough{\lstinline!user interaction points!}
\ref{user-interaction-points} and is explained in the following chapter.

@@

A project called \passthrough{\lstinline!HalbachOptimisation!}
\cite{HalbachOptimisation} implements a data analysis step and
optimizes a magnetic field that is as homogeneous as possible within a
circular section using given mechanical dimensions as input parameters
of the magnets used. For this purpose, a mutation of the magnet
positions and rotations is performed. The result is a list of positions
for each magnet.

The \passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner} opensource project, can generate basic
\gls{cad} drawings for \gls{mri} magnets in a Hallbach configuration. To
do this, the number of magnets and additional parameters for the
properties of the \gls{cad} model to be created are passed to the
function provided as input parameters using a \gls{json} file. The
result is then an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
based 3D model of the magnet holder.

@@

The input parameters of the
\passthrough{\lstinline!HalbachOptimisation!}
\cite{HalbachOptimisation} project are on the one hand the
mechanical dimensions and the number of magnets to be used. We assume
ideal magnets here. However, it should also be possible to import field
data in a more measured form later on. Using the DataAquisition
sub-step, it is possible to generate any number of ideal magnets.

@@

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the
\passthrough{\lstinline!HalbachOptimisation!}
\cite{HalbachOptimisation} project, the function signature of the
start function must be changed. This receives the result of the previous
step, in this case the generated magnet data. By optionally setting meta
data in the universal bilbiothekt data type, constants can be replaced
in the analysis function and made dynamically configurable. The return
result also corresponds to this data type so that subsequent steps are
compatible and contains the magnet data with modified position and
rotation data.

@@

The last step is to call up the
\passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
of the magnet holder. The data can also be exported as files here. To
make the project compatible, the function signatures are also adapted
here. In this case, more changes are required, as the configuration file
is loaded from the file system. This logic must be removed in order to
use the added meta data in the input parameter instead.

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly. This also fulfills the goal of
making individual user-created algorithms interchangeable. If the user
now wishes to use a different \gls{cad} algorithm instead of the
\passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner}, the other steps can simply be preserved
and only the new step needs to be implemented.

@@

In each of these categories there are then several sub-categories
divided into User Interaction Points. An overview of these is given in
the subchapters as the following. There are also introductory examples
which provide an overview of the basic functions in the
\passthrough{\lstinline!Examples!} \ref{examples} section, as well as
further examples in the online documentation
\cite{MagneticReadoutProcessingReadTheDocs}.

@@

The system is also designed to be compatible with
\passthrough{\lstinline!Extension Modules!} \ref{extension-modules},
allowing the generation of measurement data through various modules.
This extensibility enhances the versatility of the system, accommodating
diverse measurement scenarios and expanding its utility across different
domains.

@@

\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:54:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/ttyUnifiedSensorSingle",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

@@

Since there are popular data processing frameworks such as
\passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
program for mathematical calculations, Matlab are often used, the
library also supports export formats for these systems.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!.dump()!} - \gls{json}
\item
  \passthrough{\lstinline!.to\_numpy\_matrix()!} -
  \passthrough{\lstinline!Numpy!}-Array of
  \passthrough{\lstinline!data!} object with different options
\item
  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
  measurement values and temperatures
\end{itemize}

Currently, data re-import of an exported measurement is only supported
via the \gls{json} format, as an export using the other options
(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!Matlab!})loses
data during the export procedure. \}

@@

Another collection of optional modules provided by the library is the
connection of external hardware sensors. All compatible sensors that are
compatible with the firmware developed in the
\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor} chapter
are supported here. The library provides the following sensor \gls{hal}
modules for this purpose:

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
  sensors such as \passthrough{\lstinline!1D: Single Sensor!}
  \ref{d-single-sensor}
\item
  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
  such as \passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere}
\end{itemize}

@@

On the one hand, it is possible with the
\passthrough{\lstinline!MRPVisualization!} module to display measurement
data as a table or plot (e.g.~stream, line, point). This makes it
possible, for example, to visually identify outliers or trends in the
measurement data. These can also be saved as an image file. The module
is compatible with all measurement data.

In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
module, this provides functions to create 2D map plots a polar
coordinate system. This requires measurement data with additionally set
spatial coordinates. These can be generated automatically with the
\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor, or
the user must provide the spatial information from another source.

@@

In addition, the export function
\passthrough{\lstinline!.to\_numpy\_matrix!} enables further processing
of the data in the \passthrough{\lstinline!Numpy!}
\cite{harris2020array} framework, in which many other standard
analysis functions are implemented.

@@

The \passthrough{\lstinline!MRPProxy!} \ref{MRPlib_Proxy_Module.png}
module has been developed to allow forwarding and interaction with
several sensors over a network connection using a \gls{rest} interface.

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the \passthrough{\lstinline!control!}
\gls{pc}, only the \gls{ip} address or hostname of the \gls{pc} running
an \passthrough{\lstinline!MRPProxy!} instance is required
\ref{lst:mrpcli_config_using_rpc}.

@@

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table \ref{Sensor_capabilities_merging.csv}) and returned to the host
when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command is
received over network.

@@

For commands where there are several entries for
\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
\ref{Sensor_capabilities_merging.csv}, there are two possible approaches
to how the command is processed:

@@

The \passthrough{\lstinline!extend commands using an id parameter!}
strategy is used for different sensors. Each command is extended on the
\passthrough{\lstinline!Network-Proxy!} \ref{network-proxy} by another
\gls{uuid} parameter, according to the following scheme:

@@

After generating simple measurements with random values in the previous
example \ref{mrpreading}, the next step is to record real sensor data.
For this purpose, the \passthrough{\lstinline!MRPHal!} module was
developed, which can interact with all
\passthrough{\lstinline!Unified Sensor!} \ref{unified-sensor}-compatible
sensors. In the following example \ref{lst:mrpexample_hal}, an
\passthrough{\lstinline!1D: Single Sensor!} \ref{d-single-sensor} is
connected locally to the host \gls{pc}.

@@

If no hardware sensor is available or for the generation of test data,
the \passthrough{\lstinline!MRPSimulation!} module is available. This
contains a series of functions that simulate various magnets and their
fields. The result is a complete \passthrough{\lstinline!MRPReading!}
measurement with a wide range of set meta data. The example
\ref{lst:mrpexample_simulation} illustrated the basic usage. Different
variations of the \passthrough{\lstinline!generate\_reading!} function
offers the user additional parameterisation options, such as random
polarisation direction or a defined centre-of-gravity vector. The data
is generated in the background using the
\passthrough{\lstinline!magpylib!} \cite{ortner2020magpylib} library
according to the specified parameters.

@@

Once data can be acquired using hardware or software sensors, the next
step is to analyse this data. \gls{mrp} provides some simple analysis
functions for this purpose. The code example shows the basic use of the
module. The \textbf{Evaluation} \ref{evaluation} chapter shows how the
user can implement their own algorithms and add them to the library.

@@

This final example shows the use of the MRP Visualisation module, which
provides general functions for visualising measurements. This makes it
possible to visually assess the results of a measurement. This is
particularly helpful for full-sphere measurements recorded with the
\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor. The
sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
designed for these. The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement.

@@

The following example code \ref{lst:mrpexample_hallbach}, shows how a
simple hallbach magnetic ring can be generated.

This can then be used to construct a Halbach ring magnet (see chapter
\ref{Charakterisation of Permanent Magnets}) for a low-field \gls{mri}.

Eight random measurements are generated here. It is important that the
magnet type (here \passthrough{\lstinline!N45\_CUBIC\_15x15x15!}) is
specified. This is necessary so that the correct magnet cutouts can be
generated when creating the 3D model. After the measurements have been
generated, they are provided with a position and rotation offset
according to the Hallbach design and calucation scheme
\cite{HallbachMagnetDesignPaper} using the
\passthrough{\lstinline!MRPHallbachArrayGenerator!} module.

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD} file, which
contains the module generated. After computing the model using the
\passthrough{\lstinline!OpenSCAD!} \gls{cli} utility, the following
model rendering
\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
can be generated.

@@

In the other scenario, the tests are to be carried out before a new
release in the repository on the basis of
\passthrough{\lstinline!Github Actions!} \cite{GithubActions}. Here
there is the possibility to host local runner software, which then has
access to the hardware, but then a \gls{pc} must be permanently
available for this task. Instead, the hardware sensors were simulated by
software and executed via virtualisation on the systems provided by
\passthrough{\lstinline!Github Actions!}.
